\stktokens{}: Enforcing Well-bracketed Control Flow and Stack Encapsulation using Linear Capabilities

### 2018-07-09 fully-abstract-comp/popl2019/paper.tex
Added paragraph about tail calls to section 4.

@@

\section{Discussion}
\label{sec:discussion}
\begin{itemize}
\item mention that tail calls are supported through xjmp (perhaps mention earlier: when introducing scall?)
\item explain how fully abstract overlay semantics could form one pass of a verified secure compiler.
\item Sharing stack references accross component boundaries is supported
\item Other notions of well-bracketedness (specifically one would be to allow different stacks)
\end{itemize}

>>>>

\srccm{} supports tail calls.
A tail call is a call from a caller that is done executing and thus don't need to be returned to.
This means that a tail call should not reserve a slot in the return order by pushing a stack frame on the call stack, i.e.\ it should not use the built-in call.
To perform a tail call, the caller simply transfers control to the callee using \texttt{xjmp}.
The callee needs to return to the caller's caller, so the caller leaves the return pair they received for the callee to use.

@@

\section{Discussion}
\label{sec:discussion}
\begin{itemize}
\item explain how fully abstract overlay semantics could form one pass of a verified secure compiler.
\item Sharing stack references accross component boundaries is supported
\item Other notions of well-bracketedness (specifically one would be to allow different stacks)
\end{itemize}
